\begin{frame}
    \frametitle{Use GitHub for XP : Values}
    \begin{block}{Communication}
        GitHub is a collective space. With the section "Projects", the contributors can plan project, sort tasks... For every change in a work, there is commit to explain to other co-workers what has been changed. There are also Issues. It works like a chat between the co-workers.
    \end{block}\pause 
    \begin{block}{Courage} 
        With Github, every old version of a work is saved. The contributors can try major changes (like changing the architecture of the project, delete some code...) without being afraid of loosing everything.
    \end{block}
\end{frame}
\begin{frame}
    \begin{block}{Simplicity} 
        As every file and every program are saved on GitHub, their latest version are available for everyone at any moment, there's no difficulty to send informations or programs. Extreme programming involves a quick evolution of programs, so every contributor should be able to work on the latest versions.
    \end{block}\pause
    \begin{block}{Feedback} 
        The customer and the programmer are both contributors of the project on GitHub. The customer can get the latest version of the project at any moment, test this version, give feedback and ask for modifications through issues (and assign the person working on this part of the project to the issue).
    \end{block}
\end{frame}
\begin{frame}
    \frametitle{Practices}
    Extreme programming has 12 practices, grouped into four areas.\citer{wikipedia}
    \begin{columns}
        \column{0.5\textwidth}
        \begin{block}{Fine-scale feedback}
            \begin{itemize}
                \item Pair programming\citer{computerworld}
                \item Planning game
                \item Test-driven development
                \item Whole team
            \end{itemize}
        \end{block}\pause
        \begin{block}{Continuous process}
            \begin{itemize}
                \item Continuous integration
                \item Refactoring or design improvement\citer{computerworld}
                \item Small releases
            \end{itemize}
        \end{block}\pause
        \column{0.5\textwidth}
        \begin{block}{Shared understanding}
            \begin{itemize}
                \item Coding standards
                \item Collective code ownership\citer{computerworld}
                \item Simple design\citer{computerworld}
                \item System metaphor
            \end{itemize}
        \end{block}\pause
        \begin{block}{Programmer welfare}
            \begin{itemize}
                \item Sustainable pace
            \end{itemize}
        \end{block}
    \end{columns}
\end{frame}